A general framework for learning planning action models

### 2018-07-09 doc/aij18/background.tex
small updates to background section aij18 paper

\begin{table}
	\small
	\centering
	\begin{tabular}{ l | c | c | c }
		& \multicolumn{1}{c}{Input plan traces}
        & \multicolumn{1}{c}{Learned action model}
        & \multicolumn{1}{c}{Technique}     \\
		\hline			
		\multirow{2}{*}{\ARMS} & \NO states & \strips & MAX-SAT \\ & \FO actions & & \\
        \hline
        \multirow{2}{*}{\SLAF} & \POstar states  & universal quantifiers in $\eff$ & logical inference \\ & \FO actions &  & SAT solver \\
         \hline
        %\multirow{2}{*}{\SLAF} & PO states and FO actions & existential quantifiers in $\pre$ \\ & & universal quantifiers in $\eff$ &  bayesian learning \\ & & & logical filtering \\
         %\hline
		\multirow{2}{*}{\LAMP} & \PO states &  quantifiers &  Markov logic networks \\  & \FO actions & logical implications &  \\
         \hline
         \AMAN & \NO states & \strips & graphical model estimation \\ & noisy actions & & \\
         \hline
         \NOISTA & \POstar and noisy states & \strips &  classification \\ & \FO actions & & \strips \texttt{} rules derivation \\
         \hline
         \CAMA & \PO states &  \strips & crowdsourcing annotation\\ & \FO actions &  & MAX-SAT \\
         \hline
         \LOCMtwo & \NO states &  predicates and types & Finite State Machines \\ & \FO actions & & \\
         \hline
		\FAMA & \NO states & \strips &   compilation to planning\\ & \NO actions & & \\
         \hline
	\end{tabular}
	\caption{Characteristics of action-model learning approaches}
	\label{table:models_comparison1}
\end{table}

>>>>

\begin{table}
	\small
	\centering
	\begin{tabular}{ l | c | c | c }
		& \multicolumn{1}{c|}{\bf Input plan traces}
        & \multicolumn{1}{c|}{\bf Learned action model}
        & \multicolumn{1}{c}{\bf Technique}     \\
		\hline			
		\multirow{2}{*}{\ARMS} & \NO states & \strips & MAX-SAT \\ & \FO actions & & \\
        \hline
        \multirow{2}{*}{\SLAF} & \POstar states  & universal quantifiers in $\eff$ & logical inference \\ & \FO actions &  & SAT solver \\
         \hline
        %\multirow{2}{*}{\SLAF} & PO states and FO actions & existential quantifiers in $\pre$ \\ & & universal quantifiers in $\eff$ &  bayesian learning \\ & & & logical filtering \\
         %\hline
		\multirow{2}{*}{\LAMP} & \PO states &  quantifiers &  Markov logic networks \\  & \FO actions & logical implications &  \\
         \hline
         \AMAN & \NO states & \strips & graphical model estimation \\ & noisy actions & & \\
         \hline
         \NOISTA & \POstar and noisy states & \strips &  classification \\ & \FO actions & & \strips \texttt{} rules derivation \\
         \hline
         \CAMA & \PO states &  \strips & crowdsourcing annotation\\ & \FO actions &  & MAX-SAT \\
         \hline
         \LOCMtwo & \NO states &  predicates and types & Finite State Machines \\ & \FO actions & & \\
         \hline
		\FAMA & \NO states & \strips &   compilation to planning\\ & \NO actions & & \\
         \hline
	\end{tabular}
	\caption{Characteristics of action-model learning approaches}
	\label{table:models_comparison1}
\end{table}
